---
title: "Webscraping: Shopping Malls in Malaysia"
format: 
  html:
    embed-resources: true
editor: visual
message: false
warning: false
---

## Purpose/Problem

To gather information on the number of shopping malls in Malaysia, I'll webscrape data from the Wikipedia website.

### Scope

-   Using this website from [Wikipedia](https://en.wikipedia.org/wiki/List_of_shopping_malls_in_Malaysia)

## Data Extraction

-   Using this website from [Wikipedia](https://en.wikipedia.org/wiki/List_of_shopping_malls_in_Malaysia)

-   Method: Webscraping using `rvest` from R

### Load library

```{r}

library(tidyverse)
library(rvest)
library(polite)
```

### Specify url & read the html

```{r}

url <- "https://en.wikipedia.org/wiki/List_of_shopping_malls_in_Malaysia"
url_bow <- polite::bow(url)
url_bow

webpage <- scrape(url_bow)
```

### Identify & select HTML elements

```{r}

# Extract and store text content from li nodes (Wikipedia).
shopping_mall = webpage %>%
  html_nodes("body #content #bodyContent #mw-content-text .mw-parser-output ul li") %>%
  html_text() %>%
  as.character()


```

### Define a function to generate tibble (data frame)

```{r}


# Define a function to generate a tibble for a state with a subset of data from shopping_mall based on indices.
function_state <- function(State, List) {
  
  tibble(State = State,
         List = shopping_mall[eval(parse(text = List))])
  
}

# List of states with associated index ranges.
state_list <- c(
  "W.P Kuala Lumpur" = "1:85",
  "W.P Labuan" = "86:87",
  "W.P Putrajaya" = "88:90",
  "Johor" = "91:137",
  "Kedah" = "138:152",
  "Kelantan" = "153:157",
  "Melaka" = "158:171",
  "Negeri Sembilan" = "172:183",
  "Pahang" = "184:200",
  "Pulau Pinang" = "201:229",
  "Perak" = "230:246",
  "Sabah" = "247:268",
  "Sarawak" = "269:334",
  "Selangor" = "335:418",
  "Terengganu" = "419:423"
)


# Convert the named vector to a data frame with two columns
state_list_df <- enframe(state_list, name = "state", value = "indices")


# Data frame containing each state and its associated subset data from shopping_mall.
state_df <- pmap_df(.l = list(State = state_list_df$state, Indices = state_list_df$indices),
                    .f = ~ function_state(..1, ..2))



```

## Clean data

```{r}

state_df2 <- state_df %>%
  mutate(List_clean = str_replace_all(List, "\\[.*?\\]", ""))
```

## Export

```{r}

dir.create("file")

write_csv(state_df2, "file/list.csv")
```
